\begin{thebibliography}{99}
\bibitem{c11} Baker, M., Asami, S., Deprit, E., Ouseterhout, J. and Seltzer, M., 1992, September. Non-volatile memory for fast, reliable file systems. In ACM SIGPLAN Notices (Vol. 27, No. 9, pp. 10-22). ACM.
\bibitem{c7} Bhaskaran, M. S., Xu, J., Swanson, S. (2014). Bankshot: Caching slow storage in fast non-volatile memory. ACM SIGOPS Operating Systems Review, 48(1), 73-81.	
\bibitem{c12} Chen, J., Wei, Q., Chen, C. and Wu, L.F., 2013, April. A file system metadata accelerator with non-volatile memory. In Proceedings of Symposium on Mass Storage Systems and Technologies, Monterey, CA, USA (pp. 19-20).
\bibitem{c10} Condit, J., Nightingale, E. B., Frost, C., Ipek, E., Lee, B., Burger, D.,  Coetzee, D. (2009, October). Better I/O through byte-addressable, persistent memory. In Proceedings of the ACM SIGOPS 22nd symposium on Operating systems principles (pp. 133-146). ACM.
\bibitem{c13} DeBrabant, Justin, Andrew Pavlo, Stephen Tu, Michael Stonebraker, and Stan Zdonik. Anti-caching: A new approach to database management system architecture. Proceedings of the VLDB Endowment 6, no. 14 (2013): 1942-1953.
\bibitem{c3} Dulloor, S. R., Kumar, S., Keshavamurthy, A., Lantz, P., Reddy, D., Sankaran, R., Jackson, J. (2014, April). System software for persistent memory. In Proceedings of the Ninth European Conference on Computer Systems (p. 15). ACM.
\bibitem{c2} Ghandeharizadeh, S., Irani, S., Lam, J. (2015). Memory Hierarchy Design for Caching Middleware in the Age of NVM.
\bibitem{c1} Lv, Y., Cui, B., Chen, X., Li, J. (2013, October). Hotness-aware buffer management for flash-based hybrid storage systems. In Proceedings of the 22nd ACM international conference on Conference on information and knowledge management (pp. 1631-1636). ACM.	
\bibitem{c4} Persistent Memory Programming. http://pmem.io/nvml/
\bibitem{c9} Suzuki K. and Swanson S. The Non-Volatile Memory Technology Database (NVMDB). Technical Report CS2015-1011, Department of Computer Science and Engineering, University of California, San Diego, May 2015. http://nvmdb.ucsd.edu.
\bibitem{c5} Volos, H., Nalli, S., Panneerselvam, S., Varadarajan, V., Saxena, P., Swift, M. M. (2014, April). Aerie: Flexible file-system interfaces to storage-class memory. In Proceedings of the Ninth European Conference on Computer Systems (p. 14). ACM.
\bibitem{c6} Volos, H., Tack, A. J., Swift, M. M. (2011). Mnemosyne: Lightweight persistent memory. ACM SIGPLAN Notices, 46(3), 91-104.	
\bibitem{c8} Xu, J., Swanson, S. NOVA: A Log-structured File System for Hybrid Volatile/Non-volatile Main Memories.
\end{thebibliography}


% {\scriptsize  is the smallest
